---
title: "Backtest Results Report"
date: '`r strftime(Sys.time(), format = "%B %d, %Y")`'
output:
  html_document:
    df_print: paged
    toc: yes
    toc_float: yes
    toc_depth: '2'
    fig_width: 8
    fig_height: 4
params:
  results_subdirectory:
    value: x
---

```{r, include = F}
knitr::opts_chunk$set(echo = F,
                      warning = F,
                      message = F)

## Set options
options(scipen = 999, # prevent scientific notation on large numbers
        stringsAsFactors = F) # prevent R from turning everything to factors
```

# Parameters

```{r load_data, echo=F, warnings=F, message=F}
library(magrittr)
library(tidyverse)
library(lubridate)
working_directory <- here::here()
source(file.path(working_directory,"R/set_paths.R"))

results_subdirectory <- params$results_subdirectory
#results_subdirectory <- "simulated__RISK_FREE_GROWERS__random_trial_2"
results_subdirectory_path <- file.path(results_directory, results_subdirectory)

# Read in the logs
runtime_log <- read_csv(
    file.path(results_directory, results_subdirectory, "runtime_log"))
trade_history <- read_feather(
    file.path(results_directory, results_subdirectory, "trade_history.feather"))
transaction_log <- read_feather(
    file.path(results_directory, results_subdirectory, "transaction_log.feather"))
portfolio_stats <- read_feather(
    file.path(results_directory, results_subdirectory, "portfolio_stats.feather"))
```

```{r get_parameters, echo=F, warnings=F, message=F}
dirname_data <- str_split_fixed(results_subdirectory, "__", 3)
data_source <- dirname_data[1]
constituent_index <- dirname_data[2]
trial <- dirname_data[3]
num_stocks_traded <- length(unique(trade_history$symbol))
start_backtest <- min(portfolio_stats$date)
end_backtest <- max(portfolio_stats$date)
backtest_duration <- interval(ymd(end_backtest),ymd(start_backtest)) %/% months(1)
```

The backtest is specified by the following parameters:

|Parameter                 |Value|
|--|--|
|Data Source               |`r data_source`| 
|Target Equity Index       |`r constituent_index`|
|Number of Stocks Traded   |`r num_stocks_traded`|
|Algorithm Name            |`r trial`|
|Start of Backtest         |`r start_backtest`|
|End of Backtest           |`r end_backtest`|
|Backtest Duration (months)|`r backtest_duration`|
# Trade Characteristics
```{r trade_characteristics, echo=FALSE}
trade_history <- trade_history %>% dplyr::filter(quantity != 0)
final_portfolio_value <- portfolio_stats$portfolio_value[length(portfolio_stats$portfolio_value)]
max_drawdown <- round(max(portfolio_stats$drawdown_pct),2)
```

|Characteristic                       |Value|
|--|--|
|Number of Trades                     | `r length(trade_history$quantity)`|
|Total Pre-Commission Value of Trades | `r round(sum(trade_history$principal_amount),2)`|
|Total Commission Paid                | `r round(sum(trade_history$commission),2)`|
|Total Commission % of Trade Value    | `r round(sum(trade_history$commission)/sum(trade_history$principal_amount*100),2)`|
|Trade Value / Final Portfolio Value  | `r round(sum(trade_history$principal_amount/final_portfolio_value),2)`|
|Max Drawdown (%)                     | `r max_drawdown`|
|Final Value of Portfolio             | `r round(final_portfolio_value,2)`|

# Performance Characteristics
```{r}
library(xts)
library(dygraphs)
stats_xts <- xts(portfolio_stats %>% select(total_return, total_risk_free_return), order.by=portfolio_stats$date)
dygraph(stats_xts) %>% 
  dyOptions(maxNumberWidth = 20, stackedGraph = FALSE) %>%
  dyRangeSelector %>%
  dyRebase(value=100)
```

```{r}
month_ends <- tapply(portfolio_stats$date, as.yearmon(portfolio_stats$date), max)
portfolio_stats %>% filter(date %in% month_ends) %>% select(date, portfolio_value, drawdown_pct, rolling_30day_return, rolling_30day_ave_excess_return, rolling_30day_sharpe, rolling_30_day_drawdown) %>%
  mutate(drawdown_pct = round(drawdown_pct*100,2),
        rolling_30day_return = round(rolling_30day_return*100,2), 
        rolling_30day_ave_excess_return = round(rolling_30day_ave_excess_return*100,2), 
        rolling_30day_sharpe = round(rolling_30day_sharpe,2), 
        rolling_30_day_drawdown = round(rolling_30_day_drawdown*100,2))
```


```{r, eval = FALSE}
backtest_sequence <- seq(start_backtest, end_backtest, by="day")
trades <- feather::read_feather(file.path(results_path, "trade_history.feather"))
tickers <- unique(trades$symbol)
price_matrix <- data.frame(matrix(NA, ncol = 0, nrow = length(tickers)))
price_matrix$symbol <- tickers
holdings_matrix <- price_matrix


for (i in 1:length(backtest_sequence)) {
  selected_date <- backtest_sequence[i]
  #print(as.character(selected_date))
daily_holdings <-   trades %>% 
    filter(as.Date(timestamp) <= selected_date) %>%
    group_by(symbol) %>% 
    summarise(sum(quantity)) %>%
  mutate(`sum(quantity)` = symbol) %>%
  dplyr::rename(!!as.character(selected_date) := `sum(quantity)`)

holdings_matrix <- left_join(holdings_matrix, daily_holdings, by="symbol")
}

symbols <- holdings_matrix[,1]
holdings_matrix <- as.data.frame(t(holdings_matrix[,-1]))
colnames(holdings_matrix) <- symbols

# What do I want to report on?

# Annualized return
# Annualized excess return
# Risk adjusted return
# Information ratio
# Max drawdown # Weekly daily monnthly annually
# Turnover
# Ave number of trades
# Expense ratio
# Attribution: absolute return vs loss to trading
# Beta relative to benchmark

# I assume that you will also put in the PBO using the CSCV method and 
# plot the equity curves (excess wealth) against the index on a log scale 
# i.e. ln((returns-RFR)*initial weight).

# Can you confirm that your rebalancing strategy correction re-invests based on the PL.

# Do you have a transaction cost model? 
# At least square-root law: cost \approx spread + \sigma_(daily) *\sqrt(Volume/ADV)

# Summary statistics - 
# - backtest start and end date
# - index
# - number constituents
# - 

# What do we need?
# A benchmark -  define this in parameters

# Where do we save this?
# - in the results
# - a report per stock

# Over and above, we want a PBO report for the entire set of trials

#View(read_feather(file.path(results_path, "trade_history.feather")))
#View(read_feather(file.path(results_path, "submitted_trades.feather")))
#View(read_csv(file.path(results_path, "runtime_log"), col_names=F))
```